---
title: "Spatial autocorrelation tutorial"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sample Covariance
Range of values -Infinitive to + Infinitive
Standart deviation is the SQUARE
mEASURES Dispersion

#Correlation


```{r}
library(maptools)
library(spdep)
library(rgdal)
library(spData)
library(GISTools)

```


The first data set contains census tract data for eight central NY counties:

```{r}
owd <- getwd()
setwd(system.file("shapes", package="spData"))
NYcounties <- readShapeSpatial("NY8_utm18")
plot(NYcounties)
names(NYcounties)
```
Let's work on a subset of the map by focusing on Syracuse:
```{r}
unique(NYcounties$AREANAME)
syracuse <- NYcounties[NYcounties$AREANAME == "Syracuse city",]
plot(syracuse)
```
```{r}
coords <- coordinates(syracuse)
par(mfrow=c(1,1))
choropleth(syracuse, syracuse$PCTOWNHOME)
```

coords <- coordinates(syracuse)

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
